Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-07-04 MCQMC2022ChallengesQMCSoftwareArticle_revision_1.tex
Aleksei: address referee comment #4
SC: Fix references of GAIL and QMCPy MCQMC 2020

We draw on our collective experiences as
members of the academic QMC community, developers of open-source and commercial scientific software, and users of a wide range of scientific software as research scientists or data scientists. Many of the insights that we have gained have come through our development of the Guaranteed Automatic Integration Library (GAIL)~\cite{ChoEtal22a} in MATLAB and the Quasi-Monte Carlo Python library (QMCPy)~ \cite{QMCPy2020a}.

@@

Great QMC software eliminates the need for researchers to resort to  ``do-it-yourself'' for established algorithms.  The less code we have to write, the fewer errors.

@@

We next discuss the characteristics of great QMC software outlined in the introduction.  For each characteristic, we identify what is lacking and what might be done to remedy the lack.

@@

\section{Efficient} \label{CDHJS_sec:efficient}
Another obvious feature of great QMC software is computational efficiency.  This requires developers to identify bottlenecks in performance.  Intensive computations may need to be rewritten in lower-level languages, like C.  Code may need to be refactored to avoid excessive calls to memory.  As new hardware architectures arise, QMC software should adapt to take advantage of them.

>>>>

We draw on our collective experiences as
members of the academic QMC community, developers of open-source and commercial scientific software, and users of a wide range of scientific software as research scientists or data scientists. Many of the insights that we have gained have come through our development of the Guaranteed Automatic Integration Library (GAIL)~\cite{TonEtAl22a} in MATLAB and the Quasi-Monte Carlo Python library (ChoEtal22a)~ \cite{QMCPy2020a}.

@@

Great QMC software eliminates the need for researchers to resort to  ``do-it-yourself'' for established algorithms.  The less code we have to write, the fewer the errors.

@@

We next discuss the characteristics of great QMC software as outlined in the introduction.  For each characteristic, we identify potential deficiencies and suggest possible remedies.

@@

\section{Efficient} \label{CDHJS_sec:efficient}
Another obvious feature of great QMC software is computational efficiency.  This requires developers to identify bottlenecks in performance. Intensive computations may need to be rewritten in lower-level languages, like C. We have found looped randomization and point generation routines to greatly benefit from low level implementations. Code may also need to be refactored to avoid excessive calls to memory.  As new hardware architectures arise, QMC software should adapt to take advantage of them.
